---
title: 'SWEDEHEART Annual Report 2022 SwedeHF Appendix'
subtitle: "DRAFT - PREL NUMBERS 2022-11-14"
date: "Created: `r Sys.Date()`"
output:
  pdf_document:
    dev: cairo_pdf
    latex_engine: xelatex
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    number_sections: no
urlcolor: blue
linkcolor: black
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\LARGE\includegraphics[width=12cm]{logo.png}\\[\bigskipamount]}
  - \posttitle{\end{center}}
  - \usepackage{draftwatermark}
  - \usepackage{subfig}
  - \usepackage{fontspec}
  - \usepackage{fancyhdr} 
  - \pagestyle{fancy} 
  - \fancyhf{} 
  - \fancyfoot[R]{\thepage} 
  - \fancyfoot[L]{SWEDEHEART Annual Report 2022 SwedeHF Appendix} 
  - \newcommand{\epage}{\thispagestyle{empty}}
  - \renewcommand{\headrulewidth}{0pt}
  - \renewcommand{\footrulewidth}{1pt}
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
---

\epage

\newpage 
\tableofcontents 
\listoftables
\listoffigures
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, include = TRUE, comment = "",
  warning = FALSE, message = FALSE, fig.pos = "H",
  fig.path = "../output/figs/"
)
options(knitr.kable.NA = "")
```

```{r adjust_directory_if_needed, include=FALSE}
# Uncomment lines below if rmd file is placed in a subdirectory
knitr::opts_knit$set(root.dir = normalizePath("../"))
```

```{r load_project}
# 1. Set options in config/global.dcf
# 2. Load packages listed in config/global.dcf
# 3. Import functions and code in lib directory

ProjectTemplate::reload.project()

cacheon <- TRUE
```             

# Information and explanations

The information presented is based on data reported in SwedeHF until 31st of February 2022. 

The presentation is based on the date of the patients visit/admission.

Index is defined as  the first time a patient is registered in SwedeHF, not necessarily with newly diagnosed heart failure. Follow-up at 3 months can occur between 6 weeks and 6 months after index, with a mean time of 
`r formatC(mean(rsdata %>% filter(ttype == "3-month follow-up", indexyear == global_year) %>% pull(diff_timeadmission), na.rm = T) / 30.5, format = "f", digits = 1, decimal.mark = ".")` months from index for follow-up visits during `r global_year`. 

Yearly follow-up is divided into 1-year follow-up (from 6 months until 1.5 years after index), and 2+ years follow-up (from 1.5 years after index). The mean time from index until 1-year follow-up is 
`r formatC(mean(rsdata %>% filter(ttype == "1-year follow-up", indexyear == global_year) %>% pull(diff_timeadmission), na.rm = T) / 365.25, format = "f", digits = 1, decimal.mark = ".")` years and for 2+ years follow-up
`r formatC(mean(rsdata %>% filter(ttype == "2+-year follow-up", indexyear == global_year) %>% pull(diff_timeadmission), na.rm = T) / 365.25, format = "f", digits = 1, decimal.mark = ".")` years during `r global_year`. 

In cases where multiple yearly follow-up visits exist all visits have been presented. 
For 2+ years follow-up there are `r rsdata %>% filter(ttype == "2+-year follow-up" & indexyear == global_year) %>% nrow()` observations for `r rsdata %>% filter(ttype == "2+-year follow-up" & indexyear == global_year) %>% group_by(patientreference) %>% slice(1) %>% ungroup() %>% nrow()` 
unique patients during `r global_year`.  

Units with less than 10 observations in the denominator are not presented.

The R code that has generated this report is found https://github.com/KIHeartFailure/arsrapportrikssvikt2022. 

\clearpage

# Covarage

**Numerator prevalent covarage:** Individuals registered in SwedeHF, 18 years 
of age at the time, alive as of the first of January of the current year and 
registered in SwedeHF sometime during the period from the start of the register 
in 2003 up to and including the end of the December of the year in question. 
For the years where information about the registration date is available 
in SwedeHF, i.e. from 2017 onwards, only the registrations received up to and 
including March 31 of the year following the relevant year are included.

**Denominator prevalent covarage:** Individuals aged 18 and alive on January 1 of the current year, with a registration for heart failure as the main diagnosis (I11.0, I13.0, I13.2, I25.5, I42.0, I42.6, I42.7, I50.0, I50.1, I50.9) in the National Patient Register up to and including the end of December of the year in question. 

*The coverage rate for `r global_year` is based on non-quality-reviewed data from the National Board of Health and Welfare. The definition of the coverage allows occurrence in SwedeHF after occurrence in the National Patient Register, which means that the coverage is not complete for `r global_year`. The coverage rate for `r global_year` should therefore be considered preliminary.*

**Numerator incident covarage:** Individuals in SwedeHF, over 18 years of age and with first registration during the year in question or with first registration within 1 year of the first heart failure diagnosis in the National Patient Register.

**Denominator incident covarage:** Individuals registered with heart failure (I11.0, I13.0, I13.2, I25.5, I42.0, I42.6, I42.7, I50.0, I50.1, I50.9) for the first time during the current year, either in SwedeHF or in the National Patient Register.

**The coverage can be calculated in April 2022 - Figures coming.** 

---
#```{r, child = "./src/tg.Rmd"}

#```

#```{r, child = "./src/tg_bar.Rmd"}

#```
---

\clearpage

# Registration

```{r, child = "./src/regovertime.Rmd"}

```

\clearpage

```{r, child = "./src/regovertimecum.Rmd"}

```

\clearpage

# Patient characteristics

```{r, child = "./src/tabs.Rmd"}

```

\blandscape

```{r desk, cache = cacheon, fig.cap = paste0("Characteristics for patients with an index registration ", global_year), fig.show='hold', out.width="25%", fig.subcap=c('Sex', 'Age', 'NYHA class', 'LVEF'), fig.ncol=4}
piefunc(var = "sex", type = c("Index"))
piefunc(var = "age_cat", type = c("Index"))
piefunc(var = "FUNCTION_CLASS_NYHA", type = c("Index"))
piefunc(var = "ef_cat3", type = c("Index"))
```             

```{r enhetpie, cache = cacheon, fig.cap = paste0("Unit type ", global_year), fig.show='hold', out.width="25%", fig.subcap=c('Index', '3-month follow-up', '1-year follow-up', '2+-year follow-up'), fig.ncol=4}
piefunc(var = "vtype", type = c("Index"))
piefunc(var = "vtype", type = c("3-month follow-up"))
piefunc(var = "vtype", type = c("1-year follow-up"))
piefunc(var = "vtype", type = c("2+-year follow-up"))
```     

\elandscape

```{r enhetbarindex, cache = cacheon, fig.cap = paste0("Unit type for index registrations ", global_year, " by region"), fig.width=7, fig.height=8}
barfunc(var = "location", type = "Index")
```             

```{r enhetbar, cache = cacheon, fig.cap = paste0("Unit type for all registrations ", global_year, " by region"), fig.width=7, fig.height=8}
barfunc(var = "vtype", type = c("Index", "3-month follow-up", "1-year follow-up", "2+-year follow-up"))
```             

\clearpage

```{r, cache = cacheon}
qitmp <- "ferrtrans_available"
lltmp <- NULL
ultmp <- NULL
qinametmp <- "Both transferrin and ferritin reported at index"
```             

```{r ferrtranstid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(onlyindex = TRUE, starttime = global_year - 4, legplace = c(1, 90))
```             

```{r ferrtransregion, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r ferrtransenhet, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

\clearpage

# Quality Indicators

The quality indicators reported LVEF, NT-proBNP, NYHA class and QoL EQ-5D as well as planned follow-up at a heart failure clinic are defined at index. The treatment indicators, including physical exercise, are defined at the follow-up visit 3 months after index. 

The quality indicator reported follow-up visits at 3 months 
is defined within the time frame `r paste0(global_year - 1, "-07-01 - ", global_year, "-07-01")`.

\clearpage

```{r, child = "./src/summaryqi.Rmd"}

```

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_lvef"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** LVEF has been reported, either semi quantitatively or as a percentage, at index. 

**Denominator:** All patients with an index registration.

```{r lveftid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(onlyindex = TRUE)
```             

```{r lvefregion, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r lvefenhet, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_ntprobnp"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** NT-proBNP has been reported at index. For inpatients, this can 
be either at enrollment or after 24 hours.

**Denominator:** All patients with an index registration.

```{r nttid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(onlyindex = TRUE)
```             

```{r ntregion, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r ntenhet, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_nyha"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** NYHA class I, II, III, or IV has been reported at index. 

**Denominator:** All patients with an index registration.

```{r nyhatid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(onlyindex = TRUE)
```             

```{r nyharegion, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r nyhaenhet, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_qol"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** The patient's estimated state of health 
(quality of life score according to EQ-5D) has been reported at index.

**Denominator:** All patients with an index registration.

```{r qoltid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(onlyindex = TRUE)
```             

```{r qolregion, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r qolenhet, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_uppfhf"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** Those who, at the time of index, have a planned follow-up at a heart failure clinic. 

**Denominator:** All index registrations where the patient is alive at discharge and where information about planned follow-up has been reported.

```{r hfupptid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(onlyindex = TRUE)
```             

```{r hfuppfregion, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r hfuppfenhet, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_followreg3m"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** Patients who have a registered follow-up visit at 3 months (6 weeks - 6 months) after index.

**Denominator:** All index registrations where the patient is alive at 3 months.

*In the figure where follow-up visit at 3 months over time is presented only index registrations until `r paste0(global_year, "-07-01")` are included in `r global_year`. In other presentations the time interval for the index is `r paste0(global_year - 1, "-07-01 - ", global_year, "-07-01")`.*

```{r uppf3tid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(onlyindex = TRUE, legplace = c(1, 50))
```  

```{r uppf3region, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year - 1, "/", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region", startime = ymd(paste0(global_year - 1, "-07-01 - ")), stoptime = ymd(paste0(global_year, "-07-01")))
```             

```{r uppf3enhet, cache = cacheon, fig.cap = paste0(qinametmp, " ", global_year - 1, "/", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index", startime = ymd(paste0(global_year - 1, "-07-01 - ")), stoptime = ymd(paste0(global_year, "-07-01")))
```             

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_ras"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** ACE inhibitors, A2 blockers/ARBs or ARNIs have been prescribed.

**Denominator:** Patients with LVEF < 40%, who are alive at discharge and 
where information on the prescription of ACE inhibitors, A2 blockers/ARBs 
and ARNIs has been reported. LVEF is defined as the lowest measured LVEF, 
either at the presented registration or at index.

*The quality indicator is defined at the 3-month follow-up.*

```{r rastid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(ylimmin = c(70, 100), legplace = c(1, 75))
```  

\blandscape
```{r rassjhpv, cache = cacheon, fig.cap = paste0(qinametmp, " over time Sweden, hospital och primary care"), fig.show='hold', out.width="33%", fig.subcap=c('Sweden', 'Hospital', 'Primary care'), fig.ncol=3}
barsummary(unit = c("Hospital", "Primary care"))
barsummary(unit = "Hospital")
barsummary(unit = "Primary care")
```             
\elandscape

```{r rasiregion, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r rasienhet, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

```{r ras3region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up", unit = "region")
```             

```{r ras3enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up")
```             

```{r ras1region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up", unit = "region")
```             

```{r ras1enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up")
```             

```{r ras2region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up", unit = "region")
```        

```{r ras2enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up")
```        

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_arni"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** ARNI has been prescribed. 

**Denominator:** Patients where LVEF < 40%, who are alive at discharge 
and where ACE inhibitors, A2 blockers/ARBs or ARNIs have been prescribed. 
LVEF is defined as the lowest measured LVEF, either at the presented registration or at index.

*The quality indicator is defined at the 3-month follow-up.*

```{r arnitid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(legplace = c(1, 65))
```  

\blandscape
```{r arnisjhpv, cache = cacheon, fig.cap = paste0(qinametmp, " over time Sweden, hospital och primary care"), fig.show='hold', out.width="33%", fig.subcap=c('Sweden', 'Hospital', 'Primary care'), fig.ncol=3}
barsummary(unit = c("Hospital", "Primary care"))
barsummary(unit = "Hospital")
barsummary(unit = "Primary care")
```             
\elandscape

```{r arniiregion, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r arniienhet, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

```{r arni3region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up", unit = "region")
```             

```{r arni3enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up")
```             

```{r arni1region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up", unit = "region")
```             

```{r arni1enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up")
```             

```{r arni2region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up", unit = "region")
```        

```{r arni2enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up")
```        

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_bbl"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** Beta-blockers have been prescribed.

**Denominator:** Patients where LVEF < 40%, who are alive at discharge 
and where the prescription of beta-blockers has been reported. LVEF is 
defined as the lowest measured LVEF, either at the presented registration or at index.

*The quality indicator is defined at the 3-month follow-up.*

```{r bbltid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(ylimmin = c(70, 100), legplace = c(1, 75))
```  

\blandscape
```{r bllsjhpv, cache = cacheon, fig.cap = paste0(qinametmp, " over time Sweden, hospital och primary care"), fig.show='hold', out.width="33%", fig.subcap=c('Sweden', 'Hospital', 'Primary care'), fig.ncol=3}
barsummary(unit = c("Hospital", "Primary care"))
barsummary(unit = "Hospital")
barsummary(unit = "Primary care")
```             
\elandscape

```{r bbliregion, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r bblienhet, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

```{r bbl3region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up", unit = "region")
```             

```{r bbl3enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up")
```             

```{r bbl1region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up", unit = "region")
```             

```{r bbl1enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up")
```             

```{r bbl2region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up", unit = "region")
```        

```{r bbl2enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up")
```        

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_mra"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** MRA has been prescribed.

**Denominator:** Patients where LVEF < 40%, who are alive at discharge and 
where information on the prescription of MRA has been reported. LVEF is 
defined as the lowest measured LVEF, either at the presented registration  or at index.

*The quality indicator is defined at the 3-month follow-up.*

```{r mratid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc()
```  

\blandscape
```{r mrasjgpv, cache = cacheon, fig.cap = paste0(qinametmp, " over time Sweden, hospital och primary care"), fig.show='hold', out.width="33%", fig.subcap=c('Sweden', 'Hospital', 'Primary care'), fig.ncol=3}
barsummary(unit = c("Hospital", "Primary care"))
barsummary(unit = "Hospital")
barsummary(unit = "Primary care")
```             
\elandscape

```{r mrairegion, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r mraienhet, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

```{r mra3region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up", unit = "region")
```             

```{r mra3enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up")
```             

```{r mra1region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up", unit = "region")
```             

```{r mra1enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up")
```             

```{r mra2region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up", unit = "region")
```        

```{r mra2enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up")
```        

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_trippel"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** ACEI/ARB/ARNI, Beta-blockers and MRA have been prescribed.

**Denominator:** Patients where LVEF < 40%, who are alive at discharge and 
where information on the prescription of ACEI/ARB/ARNI, Beta-blockers and MRA 
has been reported. LVEF is defined as the lowest measured LVEF, 
either at the presented registration or at index.

*The quality indicator is defined at the 3-month follow-up.*

```{r trippeltid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc()
```  

\blandscape
```{r trippelsjhpv, cache = cacheon, fig.cap = paste0(qinametmp, " over time Sweden, hospital och primary care"), fig.show='hold', out.width="33%", fig.subcap=c('Sweden', 'Hospital', 'Primary care'), fig.ncol=3}
barsummary(unit = c("Hospital", "Primary care"))
barsummary(unit = "Hospital")
barsummary(unit = "Primary care")
```             
\elandscape

```{r trippliregion, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r trippelienhet, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

```{r trippel3region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up", unit = "region")
```             

```{r trippel3enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up")
```             

```{r trippel1region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up", unit = "region")
```             

```{r trippel1enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up")
```             

```{r trippel2region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up", unit = "region")
```        

```{r trippel2enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up")
```        

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_sglt2"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** SGLT-2 inhibitors has been prescribed.

**Denominator:** Patients where LVEF < 40%, who are alive at discharge and where 
information on the prescription of SGLT-2 inhibitors has been reported. LVEF is 
defined as the lowest measured LVEF, either at the presented registration or at index.

*The quality indicator is defined at the 3-month follow-up.*

```{r sglt2iregion, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r sglt2ienhet, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

```{r sglt23region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up", unit = "region")
```             

```{r sglt23enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up")
```             

```{r sglt21region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up", unit = "region")
```             

```{r sglt21enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up")
```             

```{r sglt22region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up", unit = "region")
```        

```{r sglt22enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up")
```        

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_crt"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** CRT (with or without ICD) is implanted.

**Denominator:** Patients where LVEF $\leq$ 35% (LVEF as a percentage reported) 
or < 40% (semiquantitative LVEF reported) and where information about device 
has been reported. In addition to this, left bundle branch block (LBBB) 
must be present and QRS duration must be > 130 ms. The denominator also 
includes patients with CRT implanted, regardless of QRS duration and LBBB values or 
if these are reported, which means that the proportion with CRT can be 
overestimated. LVEF, QRS duration and LBBB are defined primarily 
by what was recorded at the actual registration, and secondly, if 
missing, by what was recorded at index. 

*The quality indicator is defined at the 3-month follow-up.*

```{r crttid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc()
```  

\blandscape
```{r crtsjhpv, cache = cacheon, fig.cap = paste0(qinametmp, " over time Sweden, hospital och primary care"), fig.show='hold', out.width="33%", fig.subcap=c('Sweden', 'Hospital', 'Primary care'), fig.ncol=3}
barsummary(unit = c("Hospital", "Primary care"))
barsummary(unit = "Hospital")
barsummary(unit = "Primary care")
```             
\elandscape

```{r crtiregion, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r crtienhet, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

```{r crt3region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up", unit = "region")
```             

```{r crt3enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up")
```             

```{r crt1region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up", unit = "region")
```             

```{r crt1enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up")
```             

```{r crt2region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up", unit = "region")
```        

```{r crt2enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up")
```        

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_icd"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** ICD (with or without CRT) is implanted. 

**Denominator:** Patients where LVEF $\leq$ 35% (LVEF as a percentage reported) or < 40% (semiquantitative LVEF reported) and where information about device has been reported. LVEF is defined primarily by what was recorded at the actual registration, and secondly, if missing, by what was recorded at index.

*The quality indicator is defined at the 3-month follow-up.*

```{r icdtid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(legplace = c(1, 90))
```  

\blandscape
```{r icdsjhpv, cache = cacheon, fig.cap = paste0(qinametmp, " over time Sweden, hospital och primary care"), fig.show='hold', out.width="33%", fig.subcap=c('Sweden', 'Hospital', 'Primary care'), fig.ncol=3}
barsummary(unit = c("Hospital", "Primary care"))
barsummary(unit = "Hospital")
barsummary(unit = "Primary care")
```             
\elandscape

```{r icdiregion, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r icdienhet, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

```{r icd3region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up", unit = "region")
```             

```{r icd3enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up")
```             

```{r icd1region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up", unit = "region")
```             

```{r icd1enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up")
```             

```{r icd2region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up", unit = "region")
```        

```{r icd2enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up")
```        

\clearpage

```{r, cache = cacheon}
qitmp <- "qi_fys"
lltmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ll)
ultmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(ul)
qinametmp <- qiinfo %>% filter(qivar == qitmp) %>% pull(qiname)
```             

## Quality Indicator `r paste0(qiinfo %>% filter(qivar == qitmp) %>% pull(qino), ". ", qinametmp)` 

**Numerator:** Participation in organized physical exercise for HF has taken place.

**Denominator:** Patients where information about participation in organized 
physical exercise for HF has been reported. 

*The quality indicator is defined at the 3-month follow-up.*

```{r fystid, cache = cacheon, fig.cap = paste0(qinametmp, " over time"), fig.width=9, fig.height=7}
timefunc(legplace = c(1, 90))
```  

\blandscape
```{r fyssjhpv, cache = cacheon, fig.cap = paste0(qinametmp, " over time Sweden, hospital och primary care"), fig.show='hold', out.width="33%", fig.subcap=c('Sweden', 'Hospital', 'Primary care'), fig.ncol=3}
barsummary(unit = c("Hospital", "Primary care"))
barsummary(unit = "Hospital")
barsummary(unit = "Primary care")
```             
\elandscape

```{r fysiregion, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "Index", unit = "region")
```             

```{r fysienhet, cache = cacheon, fig.cap = paste0(qinametmp, " at index ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "Index")
```             

```{r fys3region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up", unit = "region")
```             

```{r fys3enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 3-month follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "3-month follow-up")
```             

```{r fys1region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up", unit = "region")
```             

```{r fys1enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 1-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "1-year follow-up")
```             

```{r fys2region, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by region"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up", unit = "region")
```        

```{r fys2enhet, cache = cacheon, fig.cap = paste0(qinametmp, " at the 2+-year follow-up ", global_year, " by unit"), fig.width=7, fig.height=8}
qifunc(type = "2+-year follow-up")
```        